\documentclass{ucbthesis}

% If the Grad. Division insists that the first paragraph of a section
% be indented (like the others), then include this line:
% \usepackage{indentfirst}

\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{paralist}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{array}

\usepackage[style=nature,refsection=chapter,natbib=true]{biblatex}
\addbibresource{thesis.bib}
\DefineBibliographyStrings{english}{%
  bibliography = {References}
}

\makeevenfoot{simple}{}{\thepage}{}
\makeoddfoot{simple}{}{\thepage}{}
\makeevenhead{simple}{}{}{}
\makeoddhead{simple}{}{}{}

\setsecnumdepth{subsection}
\maxtocdepth{subsection}

\begin{document}

% Declarations for Front Matter

\title{The Statistical Mechanics of Biodiversity}
\author{Andrew James Rominger}
\degreesemester{Spring}
\degreeyear{2016}
\degree{Doctor of Philosophy}
\cochairs{Professor John Harte}{Professor Rosemary G. Gillespie}
\othermembers{Professor Charles Marshall}
\numberofmembers{3}
\field{Environmental Science, Policy and Management}
\campus{Berkeley}

\maketitle
% Delete (or comment out) the \approvalpage line for the final version.
\approvalpage
\copyrightpage

\include{abstract}

\begin{frontmatter}

\begin{dedication}
\null\vfil
\begin{center}
  I dedicate this thesis to my guides and sources of solace through
  the process of completing my Ph.D.: to my mother Judy Rominger and my
  godmother Marsha Keener; to my partner Linden Schneider; and to the
  kolea \textit{(Pluvialis fulva)} and giant koa \textit{(Acacia koa)}
  of Hawaii.
\end{center}
\vfil\null
\end{dedication}


\tableofcontents
\clearpage
\listoffigures
\clearpage
\listoftables

\begin{acknowledgements}
I would like to first and foremost thank my co-Chairs, Profs. John Harte
and Rosemary Gillespie; their dedication and support to fostering my
research and advocating for my contribution to the scientific
community have been the defining feature of my graduate experience.  I
would also like to thank my outside member Prof. Charles Marshall whose
scientific curiosity and practical advice have been critical in
forging my path as a researcher.

This work would not have been possible without the support and
teamwork of many friends and collaborators.  I would like to thank
especially Prof. Pablo Marquet, Prof. Miguel Fuentes, Prof. Daniel Gruner,
Dr. Cory Merow, Prof. George Roderick, Jun Lim, Dr. Kari Goodman and Dr.
Matthew Van Dam for their camaraderie and tireless collaboration.  I
would like to thank Prof. Manisha Anantharaman, Dr. Naim Darghouth,
Dr. Danielle Christianson, Erica Newman, Dr. David Hembry, Jade Zhang
and Meredith Jabis for their friendship and support.

This work is rooted in the diversity of nature, particularly the
unique biota of Hawaii.  I am grateful to those who have dedicated
their lives to preserving and restoring that unique legacy, especially
Pat Bily, Ed Misaki and Russell Kallstrom of The Nature Conservancy
Hawaii, Rhonda Loh and Raina Kaholoa'a with the National Park Service,
and Cynthia King and Betsy Gagne with the Hawaii Department of Land
and Natural Resources.

I would also like to acknowledge my funders including the National
Science Foundation Graduate Research Fellowship, NSF DEB 1241253, the
Moore Foundation, the Department of Environmental Science, Policy
and Management and the Walker Fund at UC Berkeley.
\end{acknowledgements}

\end{frontmatter}

\addtopsmarks{headings}{}{
  \createmark{chapter}{left}{nonumber}{}{}
}

\pagestyle{simple}
\nobibintoc

\let\origChapName\chaptername
\renewcommand{\chaptername}{}
\include{intro}
\renewcommand{\chaptername}{\origChapName}
\include{chap1}
\include{chap2}
\include{chap3}
\renewcommand{\chaptername}{}
\include{conclusion}

\appendix
\include{ch1_appendix}
\include{ch2_appendix}


\end{document}